\documentclass[10pt,a4paper,ragged2e]{altacv}
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}
\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi
\definecolor{lightblue}{rgb}{0.68, 0.85, 0.9}
\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
\definecolor{olivegreen}{rgb}{0.23, 0.5, 0.21}
\definecolor{RITOrange}{HTML}{F76902}
\definecolor{Black}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{name}{olivegreen}
\colorlet{heading}{olivegreen}
\colorlet{accent}{Black}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
\addbibresource{sample.bib}

\begin{document}
\name{JOSEPH VITA}
\tagline{Rochester Institute of Technology}
\personalinfo{
  \email{jcvita2012@gmail.com}
  \phone{631-834-8067}
%  \mailaddress{Address, Street, 00000 County}
  \location{Rochester, NY}
  \github{www.github.com/Jcvita}
%  \homepage{example.com/}
%  \twitter{@joe_life}
  \newline
  \linkedin{https://www.linkedin.com/in/joseph-vita-082b32191/
  }
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Projects}
\cvprojectwithcontext{DARLing}{[ Rust ][ NIST ][ Vuln ][ SBOM ][ Language Models ]}
\begin{itemize}
\item A software platform culminating a wealth of cybersecurity frameworks of various topics into a tool that can be used both by a person to assess a system, or be implemented directly into a system to automate various assessments.  
\smallskip
\item Document your inventory of systems, software, dependencies and security policies all in one place manually or automatically. Attest to security policies and controls from standards such as NIST Special Publications, CSF, Mitre ATT\&CK framwork and CIS-CAT controls.
\smallskip
\item Assess the status and security compliance of your inventory items with Ansible. Audit dependencies for vulnerabilities. Evaluate textual attestations for advice and implementation tips using Language Models.  
\smallskip
\item Report generation allows the user to create a security report from the results of assessments on your inventory. Understand where your risks and vulnerabilities are and how to address them. 
\end{itemize}
\smallskip
\smallskip
\cvprojectwithcontext{WarpCloud}{[ Azure AD ][ Ansible ][ CosmosDB ][ DARLing ]}
\begin{itemize}
% \item GPT-3 powered essay writing assistant
% \smallskip
\item A heavily-featured enterprise cloud infrastructure built in Azure for me to practice implementing a full security stack into a cloud architecture. 
\smallskip
\item A backend API stack powered by load balanced VMs running a rust server connected to scalable CosmosDB instances, hardened with Log/Incident managing, Access control policies, SBOM tools for inventory, vulnerability and risk management, and A high Azure secure score based on security controls implemented automatically with an Ansible powered CI/CD pipeline.  
\end{itemize}
\smallskip
\smallskip
\cvprojectwithcontext{snip2clip}{[ C\# ][ Visual Studio ][ OCR API ]}
\begin{itemize}
\item Created a tool that speeds up my workflow on a daily basis by building upon the lackluster feature set of Microsoft's current snipping tool.
\smallskip
\item Used Visual Studio 2019 with C\# to make my own version of the Windows snipping tool with the Tesseract OCR API to grab any text off the screen with an image.
\end{itemize}
\smallskip
\smallskip

% \cvproject{Handwritten Digit Classifier}
% \begin{itemize}
% \item Used TensorFlow and Keras to classify handwritten digits in 28x28 images with a ~95\% accuracy
% \smallskip
% \item Taught myself the basics of machine learning and convolutional neural networks
% \smallskip
% \item Learned how to understand large dataset collection and classification 
% \smallskip
% \end{itemize}
% \cvproject{}

\cvsection{Relevant \newline Coursework}
\smallskip
\begin{itemize}
\item Calculus II, Linear Algebra, Probability \& Statistics
\smallskip
\item Cybersecurity Policy and Law, Technical Communications
\smallskip
\item Computer Science II, Programming for Information Security
\smallskip
\item Systems Administration, Routing \& Switching
\smallskip
\item Computer System Security, Network Security \& Forensics
\smallskip
\item Introduction to Cryptography, Authentication
\smallskip
\item Risk Management for Information Security
\smallskip
\item Reverse Engineering Fundamentals, Side Channel Analysis
\smallskip
\end{itemize}



%\cvsection{PERSONAL SKILLS}
%\smallskip
%\begin{itemize}
%\item Having leadership qualities.
%\smallskip
%\item Ability to work under pressure.
%\smallskip
%\item Comfortable working independently.
%\smallskip
%\item Ability to collaborate as a team and resolve conflicts 
%\end{itemize}

\clearpage

% \cvsection[page2sidebar]{Publications}

\nocite{*}

% %% If the NEXT page doesn't start with a \cvsection but you'd
% %% still like to add a sidebar, then use this command on THIS
% %% page to add it. The optional argument lets you pull up the
% %% sidebar a bit so that it looks aligned with the top of the
% %% main column.
% % \addnextpagesidebar[-1ex]{page3sidebar}

\end{document}
